Astr 513: Final Project

### 2016-04-28 Final_Project/ms.tex
Created the correlation matrix figure and added it to the text.
Renamed final.bib to msbib.bib to avoid any possible confusion.

\subsection{Covariances}
\label{sec:covariances}
\TM{A subsection that explains how the covariance matrix looks. Basically
  a brief discussion about how it was made and then a picture of the 
  {\it correlation} matrix. Example figure below.}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/clusters-randoms_noqc_correlation_subset.eps}
 \caption{Correlation matrix example. We will just have one panel.}
 \label{fig:cmatrix}
\end{figure}

\section{$\mu$ Model}
\label{sec:model}
\TM{This explains how to go from a cosmology to $\mu(z)$.}

@@

@@

\bibliography{final}

>>>>

\subsection{Covariances}
\label{sec:covariances}
\TM{A subsection that explains how the covariance matrix looks. Basically
  a brief discussion about how it was made.}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/correlation.eps}
 \caption{Correlation matrix of $\mu_0(z)$ from the
 \citet{betoule2014} sample.}
 \label{fig:cmatrix}
\end{figure}

\section{Distance Modulus Model}
\label{sec:model}
\TM{This explains how to go from a cosmology to $\mu(z)$.}

@@

\subsection{Results}
\TM{Discuss the results and show the corner plot. Example plot included.}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/corner_example.eps}
 \caption{Example corner plot.}
 \label{fig:corner}
\end{figure}

@@

\bibliography{msbib}
